A Convolutional Neural Network for Outsole Recognition\tnoteref{t1}

### 2019-06-20 paper/paper.Rnw
Slight restructuring of ROC/AUC paragraph... nothing of substance changed, but I think this might be a bit easier to read if you're not already familiar with ROC/AUC.

For each image in the test set, the ``true" labels are nine human-assigned labels of 0 or 1 corresponding to the presence or absence of each of the nine shape categories in the image. When the CNN predicts which shapes are in the image, however, it assigns a probability between 0 and 1 for each shape category, with a total of nine probabilities per test image. Thus, to determine the accuracy of the model predictions, we must select a threshold for each label to discretize the model predictions. If the threshold is too low, moderate probabilites will be more likely to exceed the threshold, which increases the true positive and false positive predictions in the test data. Conversely, if the threshold is too high, moderate probabilities will more often fail to meet the threshold, which increases the number of true and false negative predictions. An appropriate threshold must be chosen to produce a high true positive rate while also ideally keeping the false positive rate low.

Receiver Operating Characteristic (ROC) curves are a type diagnostic plot which compare the false positive rate to the true positive rate for a classification method, and the Area Under the Curve (AUC) is a summary measure which quantifies the overall accuracy of the model. Perfect prediction would be indicated by a right angle along the upper left corner of the plot, with a corresponding AUC of 1, and a diagonal line with an AUC of 0.5 would indicate that the classification method performs no better than random chance. \autoref{fig:overall-roc} shows the ROC curve for our model across all classes, and \autoref{fig:class-roc} shows the curve for each class.

>>>>

For each image in the test set, the ``true" labels are nine human-assigned labels of 0 or 1 corresponding to the presence or absence of each of the nine shape categories in the image. When the CNN predicts which shapes are in the image, however, it assigns a probability between 0 and 1 for each shape category, with a total of nine probabilities per test image. Thus, to determine the accuracy of the model predictions, we must select a threshold for each label to discretize the model predictions. If the threshold is too low, moderate probabilites will be more likely to exceed the threshold, which increases the true positive and false positive predictions in the test data. Conversely, if the threshold is too high, moderate probabilities will more often fail to meet the threshold, which increases the number of true and false negative predictions. An appropriate threshold must be chosen to produce a high true positive rate while also ideally keeping the false positive rate low. \svp{One way to set an optimal threshold is to utilize Receiver Operating Characteristic (ROC) curves, } a type diagnostic plot which compare the false positive rate to the true positive rate for a classification method. \autoref{fig:overall-roc} shows the ROC curve for our model across all classes, and \autoref{fig:class-roc} shows the curve for each class. \svp{ROC curves can be summerized by the } Area Under the Curve (AUC), which quantifies the overall accuracy of the model. Perfect prediction would be indicated by a right angle along the upper left corner of the plot, with a corresponding AUC of 1, and a diagonal line with an AUC of 0.5 would indicate that the classification method performs no better than random chance.
